A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks

### 2017-04-05 casm.tex
Added reference to supplementary material --research areas table-.OF

Even though curation and analysis work of this database is still going
on, some relevant facts about the biomedical research can be
said. Over the period of 12 years, 37 general research areas have been
defined, the three most funded research areas are \emph{chronic and
  degenerative diseases}, \emph{malignant neoplasms}, and
\emph{infectious and parasitic diseases}. The least funded area is
\emph{Ethics and medicine}. The area with the most researchers is
\emph{malignant neoplasms}. Other areas of relevance for M\'exico are
\emph{diseases related to poverty} and \emph{Health and vulnerable
  groups}. \\

>>>>

Even though curation and analysis work of this database is still going on, some
relevant facts about the biomedical research can be said. Over the period of 12
years, 37 general research areas have been defined, the three most funded
research areas are \emph{chronic and degenerative diseases}, \emph{malignant
  neoplasms}, and \emph{infectious and parasitic diseases}. The least funded
area is \emph{Ethics and medicine}. The area with the most researchers is
\emph{malignant neoplasms}. Other areas of relevance for M\'exico are
\emph{diseases related to poverty} and \emph{Health and vulnerable
  groups} {\color{red}(See Supplementary material)}.\\
